Structural-temporal neighbourhoods of posts to characterize conversations in online forums

### 2016-04-29 doc/IEEEtran/paper_IEEEformat.tex
backup

\subsubsection{Discrepancies}
The divergent number of neighbourhoods between structure-based, order-based and times-based suggests that some neighbourhoods, for instance, in time-based, might be systematically mapped to the same neighbourhoods in order-based. Or that some structure-base neighbourhoods are systematically mapped into the same time-based neighbourhoods. Figure~\ref{fig:confusion} gives a general overview of these mappings. The left figure shows, for every post, its time-based neighbourhood and its order-based neighbourhood, while the right figure shows the time-based and the structure-based. The points in the diagonal correspond to posts that have been assigned the same neighbourhood by the two compared methods.

@@

Rather than looking at where the methods agree, it is even more interesting to see where they disagree, since this will reveal whether one of the methods is incapable of detecting some interesting conversational structure.

%por aqui

Out of the diagonal, there are two rows indicating a high number of posts being assigned to the same order-based neighbourhood but to very different time-based neighbourhoods. These order-based neighbourhoods are the number 1 and the number 50. These collapse of many time-based neighbourhoods into one is significant because it happens a lot among very frequent time-based neighbourhood. Other order-based neighbourhoods that collapse many of the most frequent time-based neighbourhoods are the 22, 17, 26, 29, 49, 56, 47 and 101. 
The right figure \\TODO: expliquer... c'est time vs structure

@@

\subsubsection{Neighbourhood census}
Given a set of local structures and a graph under study, a census is a counting of how many times does each structure appear in the graph. In the context of online discussion forums, triad census has been sometimes used in the graph of users interactions are often used (in these graphs, an edge exists from user $u$ to user $v$ if $u$ wrote a post reply to some of the posts written by $v$ in some thread.) \cite{Adamic2008, Lumbreras2013}. However, triads are poor objects when studying trees since there are only three possible structures with, at most, three nodes: a single vertex, a directed dyad (reply), star (two replies to the same post) and a chain (reply and reply to the reply). On the contrary, our neighbourhoods are potentially richer structures that capture the real structure of conversations.

>>>>

\subsubsection{Discrepancies}
The divergent number of neighbourhoods between structure-based, order-based and times-based suggests that some neighbourhoods, for instance, in time-based, might be systematically mapped to the same neighbourhoods in order-based. Or similarly, that some structure-base neighbourhoods are systematically mapped into the same time-based neighbourhoods. Figure~\ref{fig:confusion} gives a general overview of these mappings. The left figure shows, for every post, its time-based neighbourhood and its order-based neighbourhood, while the right figure shows the time-based and the structure-based. The points in the diagonal correspond to posts that have been assigned the same neighbourhood by the two compared methods.

@@

Rather than looking at where the methods agree, it is even more interesting to see where they disagree, since this will reveal whether one of the methods is incapable of detecting some interesting conversational structure. In Figure~\ref{fig:confusion} some horizontals lines can be spotted specially in the lower part of the plots. These correspond to posts with different time-based neighbourhoods that are assigned the same order-based neighbourhood (left) and different time-based neighbourhoods that are assigned the same order-based neighbourhood (right). Looking for the order-based neighbourhoods that have a correspondence with a larger set of time-based neighbourhoods, we detect that these correspond to neighbourhoods 1 (77 different time-based) and 50 (57 different time-based), 17 and 18. Looking for the time-based neighbourhoods that have a correspondence with a larger set of structure-base neighbourhoods, we detect that these are neighbourhoods 10, 4, 8, 19, 14.

% Wrap-up
In retrospective, these results are not surprising. What we see is simply that structures that are often captured by one method collapse into another single structure when other method with a smaller space of structures is used. Yet, the three methods mostly agree when they find a frequent neighbourhood. But this might be due to the fact that simpler motifs tend to be in shorter threads, where there is no room for two neighbourhood methods to detect a different structure.

@@

\subsubsection{Neighbourhood census}
Given a set of local structures and a graph under study, a census is a counting of how many times does each structure appear in the graph. In the context of online discussion forums, triad census has been sometimes used in the graph of users interactions are often used (in these graphs, an edge exists from user $u$ to user $v$ if $u$ wrote a post reply to some of the posts written by $v$ in some thread.) \cite{Adamic2008, Lumbreras2013}. However, triads are poor objects when studying trees since there are only three possible structures with, at most, three nodes: a single vertex, a directed dyad (reply), star (two replies to the same post) and a chain (reply and reply to the reply). On the contrary, our neighbourhoods are potentially richer structures that respect the real structure of conversations.
